Short-time simulations of open collective quantum spin systems

### 2019-04-17 soc_squeezing/collective_paper/collective_spin.tex
plot magnitude and phase of two-time correlator, rather than real/imaginary parts; fix commentary on two-time correlator plot (in collective spin paper) to reflect recent updates

\begin{figure*}
  \centering
  \includegraphics{two_time.pdf}
  \caption{Real (solid lines) and imaginary (dashed lines) parts of
    the two-time connected correlator $C\p{t}$ defined in
    Eq.~\eqref{eq:two_time} for $N=10^4$ spins initially in the
    polarized state $\ket{\X}\propto\p{\ket\up+\ket\dn}^{\otimes N}$
    evolving under the squeezing Hamiltonians in
    Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}.  Results are shown for time
    evolution without decoherence (leftmost panel), as well as with
    decoherence at rates $\gamma_\a$ or $\Gamma_\a$,
    respectively corresponding to single-spin or collective jump
    operators $s_\a^{(j)}$ or $S_\a$.  All axes in the sub-figures are
    shared.  At short times, the correlations captured by $C\p{t}$ are
    suppressed by single-spin decay ($\gamma_-$), collective decay
    ($\Gamma_-$), and single-spin dephasing ($\gamma_\z$); these
    correlations are relatively insensitive to collective dephasing
    ($\Gamma_\z$), and can change sign or grow from spontaneous
    single-spin ($\gamma_+$) or collective ($\Gamma_+$) excitation.}
  \label{fig:two_time}
\end{figure*}

@@

Figure \ref{fig:two_time} shows the behavior of $C\p{t}$ for $N=10^4$
spins, initially in the state
$\ket\X\propto\p{\ket\up+\ket\dn}^{\otimes N}$, evolving under the
squeezing Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT} both
with and without various sources of decoherence.  The two-time
correlator $C\p{t}$ degrades at short times under certain types of
decoherence, but seems relatively insensitive to collective dephasing
(with jump operator $\hat S_\z$), and can qualitatively change
behavior or grow in the presence of single-spin or collective
excitation (with jump operators $\hat s_+^{(j)}$ or $\hat S_+$).
Figure \ref{fig:two_time} serves as an example for the type of
behavior that is accessible at short times with the TST expansion.
This example is straightforward to extend to multi-time and
out-of-time-ordered correlators, as well as equilibrium settings.

>>>>

\begin{figure*}
  \centering
  \includegraphics{two_time.pdf}
  \caption{Magnitude and phase of the two-time connected correlator
    $C\p{t}\equiv\abs{C\p{t}}\exp\sp{i\phi\p{t}}$ defined in
    Eq.~\eqref{eq:two_time} for $N=10^4$ spins initially in the
    polarized state $\ket{\X}\propto\p{\ket\up+\ket\dn}^{\otimes N}$
    evolving under the squeezing Hamiltonians in
    Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT}.  Results are shown for time
    evolution without decoherence (leftmost panel), as well as with
    decoherence at rates $\Gamma_\a$ or $\gamma_\a$, respectively
    corresponding to collective or single-spin decoherence through
    jump operators $S_\a$ or $s_\a^{(j)}$.  Collective decoherence
    rates ($\Gamma_\a$) were chosen to be comparable to the OAT
    squeezing strength $\chi$, while single-spin decoherence rates
    ($\gamma_\a$) were scaled by an additional factor of $S=N/2$ in
    order to yield comparable effects on the correlator $C\p{t}$ at
    the times shown.  At short times, the correlations captured by
    $C\p{t}$ are essentially insensitive to collective dephasing
    ($\Gamma_\z$), while the magnitude $\abs{C\p{t}}$ is suppressed by
    other forms of decoherence.  The type of decoherence (namely spin
    decay, excitation, or dephasing) leaves a signature on the phase
    $\phi\p{t}$ of $C\p{t}$.}
  \label{fig:two_time}
\end{figure*}

@@

Figure \ref{fig:two_time} shows the behavior of $C\p{t}$ for $N=10^4$
spins, initially in the state
$\ket\X\propto\p{\ket\up+\ket\dn}^{\otimes N}$, evolving under the
squeezing Hamiltonians in Eqs.~\eqref{eq:OAT}--\eqref{eq:TNT} both
with and without various sources of decoherence.  The two-time
correlations captured by $C\p{t}\equiv\abs{C\p{t}}\exp\sp{i\phi\p{t}}$
exhibit signatures of the type of decoherence present, with e.g.~clear
dependence of the phase $\phi\p{t}$ on spin decay or excitation.
Figure \ref{fig:two_time} serves as an example for the type of
behavior that is accessible at short times with the TST expansion.
This example is straightforward to extend to multi-time and
out-of-time-ordered correlators, as well as equilibrium settings.
